Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-22 Draft/Draft20181218.Rmd
.

```{r, fig.align="center"}
# TREEMAP FOR EXPORT

@@

```{r, fig.align="center"}
# Export Values in $ 
ttable=export_jTableMELTED%>%group_by(Country,year)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))
#Import Values in $
vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))

@@

  facet_wrap(~Country, scales = "free_x") +
  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 30 times",
       y="Number of Products",
       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
  theme(axis.text.x = element_text(angle=90))
```

@@

* France, Germany, UK and US are the strongest countries in terms of buying products from Turkey, adding value to these products and selling back to Turkey.

@@

* xxx

* xxx

* xxx

@@

## References
[TradeMap](https://trademap.org/Index.aspx)
[TCMB](http://tcmb.gov.tr)
[TUIK](http://www.tuik.gov.tr/)
[Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)
[R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)
[R-statistics blog](https://www.r-statistics.com/tag/transpose/)

>>>>

```{r, fig.align="center", fig.height=4, fig.width=6}
# TREEMAP FOR EXPORT

@@

```{r, fig.align="center", fig.height=6, fig.width=8 }
# Export Values in $ 
ttable=export_jTableMELTED%>%group_by(Country,year)%>%
  summarise(co_total=sum(Values,na.rm = TRUE))%>%
  arrange(desc(co_total,year))
#Import Values in $
vtable=import_jTableMELTED%>%group_by(Country,year)%>%summarise(co_total=sum(Values,na.rm = TRUE))%>%arrange(desc(co_total,year))

@@

  facet_wrap(~Country, scales = "free_x") +
  labs(title="Number of Products whose ImportUnitPrice/ExportUnitPrice ratio more than 30",
       y="Number of Products",
       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
  theme(axis.text.x = element_text(angle=90))
```

@@

* France, Germany, UK and US are the strongest countries in terms of giving strong positive trade balance with variety of product groups while India is the weakest.

@@

* Highest ratio products for India is "Yeasts, active or inactive; other dead single-cell micro-organisms" and "Pharmaceutical preparations".

* "Pharmaceutical preparations" is coming in top list for most of the countries.

* USA and UK have 47 and 42 products that have ratio more than 30 and these countries are top 2.

## K-Means Clustering

cvv

@@

cvv

## References

[TradeMap](https://trademap.org/Index.aspx)

[TCMB](http://tcmb.gov.tr)

[TUIK](http://www.tuik.gov.tr/)

[Top 50 ggplot2 Visualizations](http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html)

[R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)

[R-statistics blog](https://www.r-statistics.com/tag/transpose/)
